---
title: "WUP_Linear Model with Prediction"
author: "Emann Malik"
date: "Spring 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)
if(!require("rglwidget")) {install.packages("rglwidget");require("rglwidget")}
```
  
```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE) 
```
  
# SIMS~ARM
  
### Scatterplot
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
``` 
  
```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```
  
### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```
  
### Linear Model
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
  
The line equation is SIMS = -4.1 + 0.05 * ARM.
The model suggests that r-squared is .467 and another metric, the residual standard error, is 1.226.
  
### Prediction
  
```{r}
new <- data.frame(ARM = 88, GRIP = 94)
```
  
```{r}
predict(model.1, new, interval = "prediction", level = .95)
```
  
# SIMS~GRIP
  
### Scatterplot
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
``` 
  
```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```
  
### Numerical results

```{r}
cor(SIMS~GRIP,data=data)
```
  
### Linear Model
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```
  
The line equation is SIMS = -4.81 + 0.05 * GRIP.
The model suggests that r-squared is .405 and another metric, the residual standard error, is 1.295.   
  
### Prediction
  
```{r}
predict(model.2, new, interval = "prediction", level = .95)
```
  
# SIMS~ARM+GRIP
  
### Numerical results

```{r}
cor(SIMS~ARM+GRIP,data=data)
```
  
### Linear Model
  
```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```
  
The line equation is SIMS = -5.4 + 0.04 * ARM + 0.02 * GRIP.
The model suggests that r-squared is 0.536 and another metric, the residual standard error, is 1.144.
  
### Prediction
  
```{r}
new <- data.frame(ARM = 88, GRIP = 94)
```
  
```{r}
predict(model.3, new, interval = "prediction", level = .95)
```
  
# Compare Model1 with Model3
  
